\documentclass[10pt, letterpaper]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FONT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[condensed,math]{kurier}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% MARGINS & SPACING %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[left=1.5cm, right=1.5cm, top=1cm, bottom=1cm]{geometry}

\usepackage{setspace}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\usepackage{enumitem}
\setlist[itemize]{topsep=0pt, partopsep=0pt}
\setlist[itemize]{after=\vspace{-\baselineskip}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COLORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{xcolor}
\definecolor{darkPinkHighlight}{HTML}{E0249A}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HYPER-REF %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{color}
\usepackage{hyperref}
\hypersetup{
	pdftoolbar=true,                        
	pdfmenubar=false,                        
	pdffitwindow=false,                      
	pdfstartview={FitH},                    
	pdftitle={Graphical},    
	pdfauthor={Abhinav Chand, 
		       Tristan Freiberg,
		       Ishika Ghosh,
		       Rashmika Goswami, 
		       Astrid Olave,
		       Henry Tucker},    
	pdfcreator={Abhinav Chand, 
				Tristan Freiberg,
				Ishika Ghosh,
				Rashmika Goswami, 
				Astrid Olave,
				Henry Tucker},
	pdfproducer={Abhinav Chand, 
				 Tristan Freiberg,
				 Ishika Ghosh,
				 Rashmika Goswami, 
				 Astrid Olave,
				 Henry Tucker},
	pdfnewwindow=true,                       
	colorlinks=true,
	linkcolor={darkPinkHighlight},                      
	citecolor={darkPinkHighlight},
	filecolor={darkPinkHighlight},
	urlcolor={darkPinkHighlight},         
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% HEADERS & FOOTERS %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\title}[1]{%
	\begin{center}
		{\Large \bfseries \uppercase{#1}}
	\end{center}
}

\renewcommand{\section}[1]{%
	    \vspace{\parskip}
		{\large \bfseries\uppercase{#1}}
}

\newcommand{\itemTitle}[1]{%
	{\bfseries\uppercase{#1}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CONTEN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
\title{Graphical (think of a better title)}
	
\section{Dataset Description}
	
\begin{itemize}
\item \itemTitle{Temporal Graph:} [This is just copy-paste. Need to 
re-write, give 
credit to creators, and add citations.] The 
\href{https://tgb.complexdatalab.com/docs/nodeprop/}{\tt{tgbn-genre}} 
dataset is a bipartite and weighted interaction network between users 
and music genres. It represents users and music genres as nodes, 
where an interaction denotes a user listening to a music genre at a 
given time. Edge weights indicate the percentage of a song belonging 
to a specific genre. The dataset is derived by linking songs from the 
LastFM-song-listens dataset with music genres from the million-song 
dataset. 
\end{itemize}
	
\section{Value to Industry/Business}

\begin{itemize}
\item \itemTitle{Improved Recommendation Systems:} This project aims 
to 
enhance recommendation systems for streaming services like Spotify, 
Netflix, and YouTube. By predicting which set of music/movie/content 
genres a user will interact with the most, we can personalize 
recommendations, improve user experience, and increase user 
engagement and retention.
\end{itemize}
	
\section{Key Stakeholders}
\begin{itemize}
\item Spotify, Netflix, YouTube, and other streaming services
%\item Data analysts, data scientists, and machine learning engineers
\item End users (listeners and viewers)
\end{itemize}
	
\section{Key Performance Indicators (KPIs)}

\begin{itemize}
\item \itemTitle{MRR score:} [Brief explanation and reference]
\item Something about the
{\href{https://tgb.complexdatalab.com/docs/leader_nodeprop/\#tgbn-genre}{leaderboard}}:
 can we get on it?
\item \itemTitle{User Engagement:} Track user engagement metrics such 
as 
time spent on platform, number of interactions, and user feedback.
\item \itemTitle{Retention Rate:} Evaluate the impact of personalized 
recommendations on user retention and satisfaction.
\item \itemTitle{Business Impact:} Assess the business impact in 
terms 
of increased subscriptions, ad revenue, and customer loyalty.
\end{itemize}
	
\section{Proposal Overview}

\begin{itemize}
\item \itemTitle{Objective:} Develop a machine learning model to 
predict 
user interactions with music genres over the next week.
\item \itemTitle{Approach:} Utilize advanced graph-based algorithms 
and 
predictive modeling techniques to analyze user behavior patterns and 
preferences.
\item \itemTitle{Expected Outcome:} Deliver a scalable and accurate 
prediction system that enhances recommendation algorithms and drives 
business growth for streaming platforms.
\end{itemize}
	
\section{Conclusion}

Enhancing recommendation systems through predictive analytics can  
revolutionize the user experience in the streaming industry. By 
leveraging the 
\href{https://tgb.complexdatalab.com/docs/nodeprop/}{\tt{tgbn-genre}} 
dataset, we aim to create actionable insights and strategic 
recommendations that empower businesses to deliver personalized 
content and stay ahead in a competitive market.

\section{References}

main paper(s)

TGB website 

etc.
	
\end{document}	